Semantic High-definition Image Synthesis \\ with a Hierarchically-nested Adversarial Network

### 2017-10-23 cvpr2018.tex
merge and revision

\subsection{Overview}
In this paper, we use the following notations. Denote the image dimension, text embedding dimension and the dimension of the noise input as $I$, $T$ and $Z$, respectively. Please note that, $G$ has multiple branches and generates multiple images of different sizes and for each image size, we have a distinct $D$. For simplicity, we only describe one image size.

@@

\textbf{Variational text embedding: } Following the work of \cite{han2017stackgan}, instead of using the plan deterministic non-linear transformation of the original $\Psi_t$, we obtain the conditional vector $c$ by sampling from a Gaussian distribution $\mathcal{N}(\mu(\psi_t), \Sigma(\psi_t) )$, in which the mean $\mu(\psi_t)$ and the diagonal covariance matrix $\Sigma(\psi_t)$ are non-linear transformation of the original text embedding $\psi_t$. This type of conditional augmentation technique can be used to inject randomness to the text embedding vector $\psi_t$ to mitigate the common problem that conventional conditional GAN training paradigm usually learns to totally ignore the randomness, resulting to collapsing results lacking diversity \cite{reed2016generative}. In addition, using this kind of text embedding makes the input pure stochastic, making it more difficult for the generator to over fit the training data.

@@

\section{Dataset}

\section{Experiments}
In this section, we evaluate the proposed method both qualitatively and quantitatively on three public datasets. We denote our method as HDGAN, referring as High-definition results as well as the design of hierarchically-nested discriminators.

@@

\textbf{Dataset} We use three datasets for evaluation. \textcolor{red}{Yuanpu address}

\textbf{Evaluation metric}
\textcolor{red}{Yuanpu address}

>>>>

\textbf{Notation } In this paper, we use the following notations. Denote the image dimension, text embedding dimension and the dimension of the noise input as $I$, $T$ and $Z$, respectively. Please note that, $G$ has multiple branches and generates multiple images of different sizes and for each image size, we have a distinct $D$. For simplicity, we only describe one image size.

@@

\textbf{Variational text embedding } Following the work of \cite{han2017stackgan}, instead of using the plan deterministic non-linear transformation of the original $\Psi_t$, we obtain the conditional vector $c$ by sampling from a Gaussian distribution $\mathcal{N}(\mu(\psi_t), \Sigma(\psi_t) )$, in which the mean $\mu(\psi_t)$ and the diagonal covariance matrix $\Sigma(\psi_t)$ are non-linear transformation of the original text embedding $\psi_t$. This type of conditional augmentation technique can be used to inject randomness to the text embedding vector $\psi_t$ to mitigate the common problem that conventional conditional GAN training paradigm usually learns to totally ignore the randomness, resulting to collapsing results lacking diversity \cite{reed2016generative}. In addition, using this kind of text embedding makes the input pure stochastic, making it more difficult for the generator to over fit the training data.

@@

\section{Experiments}

\subsection{Dataset}
\textbf{Dataset} We use three datasets for evaluation. \textcolor{red}{Yuanpu address}

\subsection{Evaluation metric}
\textbf{Inception score }

\subsection{Baseline}

In this section, we evaluate the proposed method both qualitatively and quantitatively on three public datasets. We denote our method as HDGAN, referring as High-definition results as well as the design of hierarchically-nested discriminators.

@@

\textcolor{red}{Yuanpu address}
